submission

### 2024-03-04 submission.Rmd
chore: added subsections i forgot
feat: e-step explained (m-step remaining)

@@

@@

>>>>

To be able to optimize a GMM where the component means are constrained to be equal, we have to modify the classic expectation maximization algorithm to account for this specific constraint. First off, lets define the basic function for computing the density of a GMM which we will use later.

@@

Now that we have the above definition of a GMM density we can define how our new EM algorithm is going to work. As the EM algorithm is broken into two steps (E-step and M-step), we will first define the E-step.

**E-step**

As presented earlier we assume that we have some labels $Z_i$ which indicate what components model what sub-parts of the data. However, this is not something that we can know from beforehand. Thus, we compute the expected value of the statistic $\mathbb{E}[S(Z, Y) | Y ; \theta^{(t-1)}]$. Which we can denote using $\tau_{ik}^t$.

$$
\begin{align}
\tau_{ik}^t &= \mathbb{E}[S(Z,Y) | Y; \theta^{(t-1)}] \\
            &= \dfrac{\pi_k^{(t-1)} f_k(y_i;\theta^{(t-1)})}{\sum_{\mathcal{l}=0}^K \pi_k^{(t-1)} f_{\mathcal{l}} (y_i ; \theta^{(t-1)})}
\end{align}
$$

Indeed, we see that there is no need to change anything in our E-step to achieve this constraint. However, we will have to deal with this in the M-step.

**M-step**

@@

### 4.5 Model evaluation

**Task description:** Between all the previous models (the normal, the 5 mixtures of normals, and the location-scale Student) which one do you choose? Explain your methodology.

### 4.6 Expected daily return

**Task description:** Is the expected daily return different than zero?
